Scalar_M1

### 2015-05-08 models/Model_Playspace.Rmd
model update

```{r}
p = file.path("~/Desktop/Projects/scalar_implicature/")
source(paste0(p,"analysis/useful_dplyr.R"))
library("rjson")

#############   NOTES   #################
# <none, some, all> condition: the model correctly produces implicature.
# However "all"" condition is predicted to be compabitible with a 4 rating.
# This appears to be driven by several factors
# 1) High priors over 4
# 2) Fairly high compabitibiliy with All and four stars from e5
#
#
#########################################

#Basic form of the model
##############################################################################################
##########  p.Lp(r | u) ~ [p.S(u | r) * p.L(r)] / SIGMA_over_alts(p.S('u|r)*p.L(r)) ##########
##############################################################################################

r = seq(from=1, to=5) #Ratings
raw.priors = c(0.003, 0.053, 0.403, 0.387, 0.150) #Measured priors
unif.priors = rep(.2, times=5) #Uniform priors

@@

#cost function in length of chars
u.cost = function(u) {
  return(nchar(u))
}

##############################################################################################
##########                            MODEL IMPLEMENTATION                          ##########
##############################################################################################
#Key------------------------>
#u = utterance [string]
#alts = alternative utterances
#r = rating index [1-5]
#d.info = informativity judgements
#Key------------------------>

@@

#normalized posterior---------------------------------->
norm.post = function(utt, rating, s.matrix, priors) {
  nn = nn.post(utt, rating, s.matrix, priors)
  norm = 0
  for (i in 1:5) {
    norm = norm + nn.post(utt, i, s.matrix, priors)
  }
  return(nn / norm)
}
speaker.prob = function(utt, rating, s.matrix)
##############################################################################################
##########                              DATA / PLOTS                                ##########
##############################################################################################
#priors
qplot(c(1:5), raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="Priors over ratings")

#SOME ---------------------------------------------->
d.some.unif.priors = sapply(1:5, FUN=function(i){
  norm.post("some", i, scale.matrix, unif.priors)})
d.some.raw.priors = sapply(1:5, FUN=function(i){
  norm.post("some", i, scale.matrix, raw.priors)})
qplot(c(1:5), d.some.raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="Some Posteriors")

#ALL ------------------------------------------------>
d.all.raw.priors = sapply(1:5, FUN=function(i){
  norm.post("all", i, scale.matrix, raw.priors)})
d.all.unif.priors = sapply(1:5, FUN=function(i){
  norm.post("all", i, n.scale.matrix, unif.priors)})
qplot(c(1:5), d.all.raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="All Posteriors, Raw priors")
qplot(c(1:5), d.all.unif.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="All Posteriors, Uniform priors")
```

>>>>

Preliminaries.

```{r}
rm(list=ls())
p = file.path("~/Projects/Scalar Implicature/scalar_implicature/")
source(paste0(p,"analysis/useful_dplyr.R"))
library(rjson)
```

## Notes
* <none, some, all> condition: the model correctly produces implicature.
* However "all"" condition is predicted to be compabitible with a 4 rating.
* This appears to be driven by several factors
  * 1) High priors over 4
  * 2) Fairly high compabitibiliy with All and four stars from e5

## Basic form of the model

$$ p_{L_p} (r \mid u) \propto \frac{p_S(u | r) p_{L_0}(r)}{\sum_{u' \in alts}{p_S(u' \mid r) p_{L_0}(r)}}$$

```{r}
r = seq(from=1, to=5) #Ratings
raw.priors = c(0.003, 0.053, 0.403, 0.387, 0.150) #Measured priors
unif.priors = rep(.2, times=5) #Uniform priors

@@

#cost function in length of chars
u.cost = function(u) {
  return(nchar(u))
}
```

## MODEL IMPLEMENTATION

Key:
* u = utterance [string]
* alts = alternative utterances
* r = rating index [1-5]
* d.info = informativity judgements

```{r}

@@

#normalized posterior---------------------------------->
norm.post = function(utt, rating, s.matrix, priors) {
  nn = nn.post(utt, rating, s.matrix, priors)
  norm = 0
  for (i in 1:5) {
    norm = norm + nn.post(utt, i, s.matrix, priors)
  }
  return(nn / norm)
}

```

## DATA / PLOTS

Priors
```{r}
qplot(c(1:5), raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="Priors over ratings")
```

SOME
```{r}
d.some.unif.priors = sapply(1:5, FUN=function(i){
  norm.post("some", i, scale.matrix, unif.priors)})
d.some.raw.priors = sapply(1:5, FUN=function(i){
  norm.post("some", i, scale.matrix, raw.priors)})

qplot(c(1:5), d.some.raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="Some Posteriors")
```

ALL
```{r}
d.all.raw.priors = sapply(1:5, FUN=function(i){
  norm.post("all", i, scale.matrix, raw.priors)})
d.all.unif.priors = sapply(1:5, FUN=function(i){
  norm.post("all", i, n.scale.matrix, unif.priors)})

qplot(c(1:5), d.all.raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="All Posteriors, Raw priors")
```
